Deep Learning Predictions of Antenna Geometry for Desired Far-Field Signals in Terahertz Leaky Wave Antennas

### 2022-07-04 paper/paper.tex
pre cleaning up!

\documentclass[11pt]{article}
\usepackage[margin  = 1in]{geometry}
\usepackage{hyperref}
\usepackage{amsmath} 
\usepackage{graphicx}
\usepackage{float}
\usepackage{subcaption}
\bibliographystyle{naturemag}

@@

\noindent Examples of direct problems include approximating an antenna's output given a geometry \cite{8608745} or modeling a metasurface \cite{Nadell:19}, which could take a finite-element model hours or longer to solve, limiting real-time simulation and design. Inverse problem considers the opposite direction, for example reconstructing an image from scattered light \cite{Sun:18}. There have been many applications of neural networks to communications-related problems, for example, in the optimization of massive multiple-input multiple-output (MIMO) systems to improve signal reconstruction quality \cite{8322184} or physical layer design \cite{DBLP:journals/corr/OSheaEC17}. \emph{MORE EXAMPLES HERE?} \\

@@

\noindent where $k_0$ is the free space wave number, $h$ is the plate separation, and $\Lambda$ is the slot periodicity. Each different mode peaks at some given angle $\theta$ defined by $\theta=\cos^{-1}(\beta_p/k_0)$, given that the excited modes can be consider fast-wave (i.e. $|\beta_p|>k_0$ ). Our primary objective is to generate multiple beams with specific magnitudes at specific locations, which we demonstrate in Figure 2a using numerical simulations of four periodic waveguides with different periodicities. Each different period has peaks at different angles. Therefore, instead of a periodic geometry, we consider a non-uniformly periodic array of slots in order to exploit multiple periodicities and thus excite multiple modes, producing peaks at multiple angles. By Fourier decomposition, we note that any non-periodic slot design can be viewed as a linear combination of periodic designs $\beta_p$, each peaking at an angle $\cos(\theta)=\beta_p/k_0$. The strength (amplitude) of individual peaks can be related to the Fourier coefficients of this decomposition. Our discretized geometry imposes limits on the possible excited Floquet modes, by constraining the values of $\Lambda$. Indeed, due to the discretization, the possible $\Lambda$ for a total slot length $\ell$ and sub-slot length $\xi$ given by:

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=6in]{figures/theorypdf}
	\caption{Floquet theory predictions for geometry. a) Numerical simulations for uniformly periodic LWAs with four different values of $\Lambda$; each peaks at different angles, indicating how we use superposition of modes to generate a wide array of possible angles. Note that all periods have a maximum around 48 degrees, which is the primary mode for a LWA of these dimensions. b) The possible Floquet modes from any linear combination of modes predicted by Equation 1; as expected, the positive modes occur in forward scattering and the negative modes in back-scattering. }
\end{figure}

\noindent Figure 2 indicates that modulating the periodicity of the geometry we describe enables far-field peak formation at a wide variety of angles, indicating that is a useful regime in which to design a slot based on some desired far-field signal. Solving this inverse problem (i.e. calculating the slot for some given far-field profile), however, is difficult; deriving an analytical expression for a complicated regime is difficult if not impossible, and solving numerically would require iteration through multiple antenna designs until arriving at an optimal solution, essentially searching for one needle in a haystack of $2^{32}$ possible antenna geometries. This is where the idea of a neural network model enters -- deep learning methods are effective at describing nonlinear relationships of complex systems simply by providing training data from which the model can ``learn''. Thus, we build a model that predicts the slot geometry for some input of a desired far-field signal. \\

@@

\noindent 20,000 instances of COMSOL simulation data were generated as the data source for the deep neural network, with a test-train split of 80-20 \cite{molecules26041111}. The network, which is built with TensorFlow \cite{tensorflow2015-whitepaper}, a popular deep-learning library, has one convolutional layer for feature extraction connected to six sequential fully-connected layers, each of which have 2000 neurons and use a LeakyReLU activation function with $\alpha = 0.1$. The model uses the Adam optimizer and has a learning rate of 0.0001 and predicts the output of each individual sub-slot with a sigmoid activation function indicating the probability that a given sub-slot should be transparent. The model is visualized in Figure 3. \\

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=6in]{figures/fig1pdf}
	\caption{Neural network architecture schematic. The amplitudes at the angle of each possible Floquet mode are used as the input data and passed through one convolutional layer and six hidden layers within a neural network architecture to predict the  slot design that will yield the closest possible signal. Full network parameters can be found in the code}
\end{figure}

\noindent The tricky part of the inverse problem, as we consider here, is finding an appropriate loss function -- the primary objective is to generate a slot that minimizes the difference in signal compared to what is desired, but in order to use this basis as our loss function, we would need to compute the far-field signal for each new slot we generate as we train the model, which would be extraordinarily (and unfeasibly) computationally expensive. Thus, instead, we turn to the naive idea of making the generated slot look as similar to the given training slot for a given peak profile as possible, although not ideal (one can easily imagine a situation where a slot design was simply offset by 1 in either direction, from which we would expect a very similar response yet would likely score poorly in accuracy). Modified loss functions that introduced a convolutional element in order to emphasize spatial relationships and not exact locations of a sub-slot were tested but performed poorly compared to the naive loss funcrion. Given that this is a binary classification problem for each sub-slot, we use binary cross-entropy (BCE) loss. \\

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=6in]{figures/setuppdf}
	\caption{a) sample hot-stamped binary antenna; b) sample hot-stamped greyscale antenna; c) experimental setup, where the LWA is mounted on a rotation stage between a transmitter and receiver connected to a terahertz time-domain spectroscopy system}
\end{figure}

@@

For some given far-field response, the compiled model extracts the Floquet peaks and predicts each individual sub-slot's probability of being transparent (i.e. a value close to 0 indicates the sub-slot should be metal, whereas a value close to 1 indicates a transparent sub-slot) using a sigmoid activation function. In Figure 5, for two random peak profiles inputted into the model, the objective signal and the slot that created it are shown alongside the slot design that the model predicted and the far-field pattern that slot actually generates. Both of these predicted slots look quite similar to the objective slot, although they are not exact matches; of the 4000 simulations used for testing the model's performance, 70.9\% of sub-slots were predicted correctly as transparent or metallic, indicating substantial predictive value over the baseline of 50\%.

@@

\noindent This procedure enables us to measure the performance of the model by a more useful metric than how similar the slot geometry is; rather, we can compare the similarity of the objective far-field response with the far-field response of the slot geometry the model predicts is optimal based on the objective input. Using the mean square error computed in Step 3, we plot a histogram of MSE in Figure 6a and compare it to a control where we compute the MSE between two random signals. The shape of the distribution in Figure 6a matches that of similar work \cite{Nadell:19} and is significantly better than the control (i.e. the similarity between two random far-field patterns), indicating substantial predictive value. The right panel of Figure 6 shows the wide range of normalized far-field power in dB at each possible peaks. The seventh peak, which occurs at 48 degrees, is always the highest because that is the primary mode of an LWA regardless of periodicity.

\begin{figure}[H]
	\includegraphics[width=6.5in]{figures/fig6apdf}
		\caption{a) Mean square error (MSE) histogram. The horizontal displacement between the two histograms shows that the model predicts significantly more accurate antenna geometries than the control. b) Box plot of the possible values at each peak. A wide array of values are possible at each peak, indicating that the model may be effective over a wide range of far-field signals.}
\end{figure}

\noindent Overall, we see that most Floquet peaks have a wide range of possible values, indicating that our model can be used to predict an ideal geometry for a wide range of far-field patterns. The two examples in Figure 5 showcase the ability of the model to produce reasonable slots that approximate the desired far-field signal. These two cases showcase some of the better performance of the model, and like most models, not all inputs will yield a useful result. However, even for objective signals that yield substantially higher values of mean-square error, the overall peak behavior is often well-preserved, albeit with less exact results and more missed peaks, as would be expected from a higher MSE. Indeed, the goal of this investigation is to demonstrate the usefulness of neural networks for predicting antenna geometry, not to build a perfectly-tuned model. \\

@@

\begin{figure}[H]
	\centering
	\includegraphics[height=2.4in]{figures/477exppdf2}
	\caption{Comparison of experimental and numerical results for non-uniform periodic slot. The experimental signal is what was measured for the given slot using TDS, the expected is what we expect for the antenna geometry the model predicts, and the objective is the desired signal.}
\end{figure}

@@

\subsection*{Grey Sub-Slot Scheme}
%
%\noindent This second scheme significantly expands the scope of the problem because each sub-slot can take one of five values instead of just two: fully metallic, 25\% transparent, 50\% transparent, 75\% transparent, and 100\% transparent. We again generate approximately 20,000 samples using numerical simulation where each sub-slot can take on these values using a transition boundary layer. This significantly increases the number of degrees of freedom within the model, as we see in the right panel of Figure 8 below; the range of values at each peak is broader than is seen than in Figure 4.
%
%\begin{figure}[H]
%	\includegraphics[width=6.5in]{figures/histboxgreypdf}
%		\caption{The left panel shows the mean square error histogram and verifies the model's predictive value while the right panel shows the wide array of possible values at each peak.}
%\end{figure}
%
%\noindent The left panel of Figure 8 shows the mean square error histogram for the 500 sets of testing data for which we numerically solved for the predicted slot's far-field pattern in order to compare its similarity to the objective. While the model performs similarly to the binary case (except for a slightly longer tail here), the control MSE histogram broadens and moves to the right. This means that our model performs better relative to the control with the greyscale scheme compared to the binary scheme, which is not unexpected given the increased degrees of freedom at play and the strength of neural network models at uncovering complex non-linear relationships.  \\
%
%
%\noindent Like before in Figure 5, we can plot some of the model-generated slots and the resulting far-field patterns in order to get an idea of what sort of slots the model is producing, which we plot in Figure 9 below. Overall, we see close agreement between the objective and ML-predicted slots, particularly at the largest peaks and the overall profile of the wave.
%
%%\begin{figure}[H]
%%	\centering
%%	\subfloat{{\includegraphics[height=2.1in]{figures/grey_example_71.eps}}}
%%	\subfloat{{\includegraphics[height=2.1in]{figures/grey_example_127.eps}}}
%%	\caption{Model predictions for two different peak profiles using the greyscale scheme. The left slot design is the randomly generated greyscale slot used to generate the objective, the center plot shows the ideal transparency of each sub-slot, and the right plot shows those rounded into the buckets used in the simulation. The MSEs of the left and right predictions are 0.0127 and 0.0113.}
%%\end{figure}
%
%\noindent As before, we are interested in comparing the results of our model and numerical simulations to experimental data. However, this is slightly more complicated experimental method -- we need to actually experimentally generate semi-transparent slots. We do this by using the aforementioned hot-stamping technique but instead of using black ink for metallic slots and the absence of ink for transparent slots, we calibrate our TDS system using ``grey'' slots, the idea being that changing the ink color within the greyscale spectrum will directly correlate with the amount of metal deposited on the surface of the antenna. We first calibrate shades of grey with transmission values, then using the shades of grey that conform to 25\%, 50\%, and 75\% transparency, we produce our LWAs using the exact same methodology as in the binary case.

@@

\noindent There remain many areas of further exploration; we present a baseline model that serves as a proof-of-concept, but it could surely be further improved and optimized by generating more training data and extensively tuning the model hyperparameters. Additionally, we explore only one additional method of modulation: making some sub-slots partially transparent. It is easy to conceive of other ideas, such as modulating the width of each sub-slot or further increasing the number of intermediate grey steps, all of which serve as significant areas of further research from both modeling and experimental perspectives.

\section*{Data Availability}
The large amount of training data makes its sharing prohibitively difficult but can be shared upon reasonable request from the authors.

@@

\section*{Funding}
Research funds de Quebec and NSF grants?

>>>>

\documentclass[11pt]{article}
\usepackage[margin  = 1in]{geometry}
\usepackage{hyperref}
\usepackage{amsmath} 
\usepackage{graphicx}
\usepackage{float}
\usepackage{subcaption}
\bibliographystyle{naturemag}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}
\rhead{DRAFT MANUSCRIPT (1 July 2022)}
\lhead{Neronha et al. (2022)}

@@

\noindent Examples of direct problems include approximating an antenna's output given a geometry \cite{8608745} or modeling a metasurface \cite{Nadell:19}, which could take a finite-element model hours or longer to solve, limiting real-time simulation and design. Inverse problem considers the opposite direction, for example reconstructing an image from scattered light \cite{Sun:18}. There have been many applications of neural networks to communications-related problems, for example, in the optimization of massive multiple-input multiple-output (MIMO) systems to improve signal reconstruction quality \cite{8322184}, physical layer design \cite{DBLP:journals/corr/OSheaEC17}, or predicting channel state information \cite{8395053}. Neural networks and deep learning are particularly useful and interesting in communications applications because of their strength in predicting complex, nonlinear, and multivariate relationships that underly electromagnetics \cite{raissi2018deep}.\\

@@

\noindent where $k_0$ is the free space wave number, $h$ is the plate separation, and $\Lambda$ is the slot periodicity. Each different mode peaks at some given angle $\theta$ defined by $\theta=\cos^{-1}(\beta_p/k_0)$, given that the excited modes can be consider fast-wave (i.e. $|\beta_p|>k_0$ ) \cite{6556051}. Our primary objective is to generate multiple beams with specific magnitudes at specific locations, which we demonstrate in Figure 2a using numerical simulations of four periodic waveguides with different periodicities. Each different period has peaks at different angles. Therefore, instead of a periodic geometry, we consider a non-uniformly periodic array of slots in order to exploit multiple periodicities and thus excite multiple modes, producing peaks at multiple angles. By Fourier decomposition, we note that any non-periodic slot design can be viewed as a linear combination of periodic designs $\beta_p$, each peaking at an angle $\cos(\theta)=\beta_p/k_0$. The strength (amplitude) of individual peaks can be related to the Fourier coefficients of this decomposition. Our discretized geometry imposes limits on the possible excited Floquet modes, by constraining the values of $\Lambda$. Indeed, due to the discretization, the possible $\Lambda$ for a total slot length $\ell$ and sub-slot length $\xi$ given by:

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=6in]{figures/theorypdfslots}
	%we still have theorypdf.pdf which was that weird scatter plot... do we like that? maybe not the best way to represent but I can't think of a better way.
	\caption{Floquet theory predictions for different geometries of uniform periodicities. a) Numerical simulations for uniformly periodic LWAs with four different values of $\Lambda$; each peaks at different angles, indicating how we use superposition of modes to generate a wide array of possible angles. Note that all periods have a maximum around 48 degrees, which is the primary mode for a LWA of these dimensions. b) The slots used to generate these uniform periodicities; the light sub-slots indicate metal and the darker sub-slots are transparent.}
\end{figure}

\noindent Figure 2 indicates that modulating the periodicity of the geometry we describe enables far-field peak formation at a wide variety of angles, indicating that is a useful regime in which to design a slot based on some desired far-field signal. Solving this inverse problem (i.e. calculating the slot for some given far-field profile), however, is difficult; deriving an analytical expression for a complicated regime is difficult if not impossible, and solving numerically would require iteration through multiple antenna designs until arriving at an optimal solution, essentially searching for one needle in a haystack of $2^{32}$ possible antenna geometries. This is where the idea of a neural network model enters -- deep learning methods are effective at describing nonlinear relationships of complex systems simply by providing training data from which the model can ``learn'' \cite{raissi2018deep}. Thus, we build a model that predicts the slot geometry for some input of a desired far-field signal. \\

@@

\noindent 20,000 instances of COMSOL simulation data were generated as the data source for the deep neural network, with a test-train split of 80-20 \cite{molecules26041111}. The network, which is built with TensorFlow \cite{tensorflow2015-whitepaper}, a popular deep-learning library, has one convolutional layer for feature extraction \cite{albawi2017understanding} connected to six sequential fully-connected layers, each of which have 2000 neurons and use a LeakyReLU activation function with $\alpha = 0.1$ \cite{nair2010rectified}. The model uses the Adam optimizer \cite{kingma2014adam} and has a learning rate of 0.0001, batch size of 128, and trains the model over 35 epochs \cite{smith2018disciplined} and predicts the output of each individual sub-slot with a sigmoid activation function indicating the probability that a given sub-slot should be transparent. The model is visualized in Figure 3. \\

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=5.2in]{figures/fig1pdf}
	\caption{Neural network architecture schematic. The amplitudes at the angle of each possible Floquet mode are used as the input data and passed through one convolutional layer and six hidden layers within a neural network architecture to predict the  slot design that will yield the closest possible signal. Full network parameters can be found in the code}
\end{figure}

\noindent The tricky part of the inverse problem, as we consider here, is finding an appropriate loss function -- the primary objective is to generate a slot that minimizes the difference in signal compared to what is desired, but in order to use this basis as our loss function, we would need to compute the far-field signal for each new slot we generate as we train the model, which would be extraordinarily (and unfeasibly) computationally expensive. Thus, instead, we turn to the naive idea of making the generated slot look as similar to the given training slot for a given peak profile as possible, although not ideal (one can easily imagine a situation where a slot design was simply offset by 1 in either direction, from which we would expect a very similar response yet would likely score poorly in accuracy). Modified loss functions that introduced a convolutional element in order to emphasize spatial relationships and not exact locations of a sub-slot were tested but performed poorly compared to the naive loss funcrion. Given that this is a binary classification problem for each sub-slot, we use binary cross-entropy (BCE) loss. \cite{10.1145/1102351.1102422} \\

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=6in]{figures/setuppdf2}
	\caption{a) sample hot-stamped binary antenna; b) sample hot-stamped greyscale antenna; c) experimental setup, where the LWA is mounted on a rotation stage between a transmitter and receiver connected to a terahertz time-domain spectroscopy system}
\end{figure}

@@

For some given far-field response, the compiled model extracts the Floquet peaks and predicts each individual sub-slot's probability of being transparent (i.e. a value close to 0 indicates the sub-slot should be metal, whereas a value close to 1 indicates a transparent sub-slot) using a sigmoid activation function. In Figure 5, for two random peak profiles inputted into the model, the objective signal and the slot that created it are shown alongside the slot design that the model predicted and the far-field pattern that slot actually generates.

@@

\noindent This procedure enables us to measure the performance of the model by a more useful metric than how similar the slot geometry is; rather, we can compare the similarity of the objective far-field response with the far-field response of the slot geometry the model predicts is optimal based on the objective input. Using the mean square error computed in Step 3, we plot a histogram of MSE in Figure 6a and compare it to a control where we compute the MSE between two random signals. The shape of the distribution in Figure 6a matches that of similar work \cite{Nadell:19}. We conduct a two-sided Z-test -- the requirements of which are satisfied given that the histogram indicates a normal distribution, there are 30+ samples, and samples are independent -- and confirm the model's predictive value is statistically significant with a p-value of 2.91e-89, which indicates significance at a very low value of $\alpha$. The average MSE of the model results is 0.0361, and the subslot prediction accuracy is 70.0\%, which is above the baseline value of fifty percent at which there would be no predictive value. 
\begin{figure}[H]
	\includegraphics[width=6.5in]{figures/fig6apdf}
		\caption{a) Mean square error (MSE) histogram. The horizontal displacement between the two histograms shows that the model predicts significantly more accurate antenna geometries than the control and is confirmed by a Z-test. b) Box plot of the possible values at each peak. A wide array of values are possible at each peak, indicating that the model may be effective over a wide range of far-field signals.}
\end{figure}

\noindent Figure 6b shows the wide range of normalized far-field power in dB at each possible peaks. The seventh peak, which occurs at 48 degrees, is always the highest because that is the primary mode of an LWA regardless of periodicity. Overall, we see that most Floquet peaks have a wide range of possible values, indicating that our model can be used to predict an ideal geometry for a wide range of far-field patterns. The two examples in Figure 5 showcase the ability of the model to produce reasonable slots that approximate the desired far-field signal. These two cases showcase some of the better performance of the model, and like most models, not all inputs will yield a useful result. However, even for objective signals that yield substantially higher values of mean-square error, the overall peak behavior is often well-preserved, albeit with less exact results and more missed peaks, as would be expected from a higher MSE. Indeed, the goal of this investigation is to demonstrate the usefulness of neural networks for predicting antenna geometry, not to build a perfectly-tuned model. \\

@@

\begin{figure}[H]
	\centering
	\includegraphics[height=2.1in]{figures/477exppdf2}
	\caption{Comparison of experimental and numerical results for non-uniform periodic slot. The experimental signal is what was measured for the given slot using TDS, the expected is what we expect for the antenna geometry the model predicts, and the objective is the desired signal.}
\end{figure}

@@

\subsection*{Grey Sub-Slot Scheme}

\noindent This more advanced schema significantly expands the scope of the problem because each sub-slot can take one of three values instead of just two: 0\% transparent (i.e. fully metallic), 50\% transparent, and 100\% transparent. We again generate approximately 20,000 samples using numerical simulation where each sub-slot can take on these values using a transition boundary layer. This significantly increases the number of degrees of freedom within the model, which we would expect would allow us to generate slots for a wider array of potential signals.  This is suggested by Figure 9b below; the range of values at each peak is broader in the grey model than for the binary model.
%
\begin{figure}[H]
	\includegraphics[width=6.5in]{figures/histandboxgreyoverlay}
		\caption{a) The mean square error histogram for both the grey model performance and a control sample. The horizontal offset indicates the model's predictive value and is confirmed by a Z-test. b) A box plot of possible normalized power values for both models. The grey model allows for a wider array of values, as we expect from the increase degrees of freedom in this model.}
\end{figure}

\noindent As with the binary case, we plot a histogram of the model results in Figure 9a and again note the horizontal offset between the model and control. We again conducted two-sided z-test between two samples with the same justifications and again establish a statistically significant difference with p-value of 1.86e-72, indicating significance at a very low value of $\alpha$ (albeit the p-value here is higher than for the binary model, although both are very lower). The average MSE is 0.0434, which is higher than in the binary case, and the sub-slot accuracy is 48.1\%; while higher than the base 33.3\% one would expect given there is a 1/3 chance of correctly guessing, this accuracy is lower than in the binary case. This is not unexpected; due to computational constraints, we generate the same number of training samples as the binary case despite the increased degrees of freedom ($3^{36}$ instead of $2^{36}$, a significant increase). That means in the grey schema, we have a smaller amount of data in relation to the number of possible outcomes, which may explain the decreased accuracy.

\noindent As before, we are interested in comparing the results of our model and numerical simulations to experimental data. However, this is slightly more complicated experimental method -- we need to actually experimentally generate semi-transparent slots. We do this by using the aforementioned hot-stamping technique but instead of using black ink for metallic slots and the absence of ink for transparent slots, we calibrate our TDS system using ``grey'' slots, the idea being that changing the ink color within the greyscale spectrum will directly correlate with the amount of metal deposited on the surface of the antenna. We first calibrate shades of grey with transmission values to determine the greyscale value between 0 and 255 that yields approximately 50\% transmission; we find it to be 109. We then produce our LWAs using the exact same methodology as in the binary case.

\begin{figure}[H]
	\centering
	\includegraphics[height=2.4in]{figures/greyexperiment}
		\caption{(34 in set). An example of the grey model's performance and comparison to experimental results. The left slot design shows the slot used to produce the objective far-field signal and the right slot design shows the model's prediction. The polar plot shows the far-field signals computed numerically for each of these slots, overlaid with the experimental results collected using TDS. The numerical predicted and objective far-field signals closely agree with an MSE of 0.0311, despite slots that while sharing similarities are somewhat different, and match the experimental data well.}
\end{figure}

\noindent An example of the model's predictive performance is shown in Figure 10, along with a comparison to the experimental results for the predicted slot collected using the method described in the previous paragraph with the TDS setup described in Figure 4c. We draw a handful of conclusions from Figure 10. First, for this example, which has an MSE approximately in the center of the histogram and thus can be considered roughly average performance for the model, the predicted and objective far-field signals generally agree quite well and have very similar shapes, despite having slot patterns that are not exactly the same, as we would expect from Floquet theory -- there are many ways to achieve a linear combination of periodicities. Secondly, the experimental results agree fairly closely with the numerical predicted values. While there are some differences particularly in the backwards direction, it is important to remember that these results were collected using hot-stamping, an inherently inexact rapid-prototyping technique that is particularly imprecise given that we can only generate an approximately 50\% transparent slot subject to the whims of the laster printer, in addiction to the difficulty of measuring back-reflection at large angles $\geq 140$ degrees.  Overall, the experiment confirms the validity of producing LWA metasurfaces in this fashion, and we expect the experimental accuracy to be higher using more advanced methods of producting metasurfaces.

@@

\noindent There remain many areas of further exploration; we present a baseline model that serves as a proof-of-concept, but it could surely be further improved and optimized by generating more training data and extensively tuning the model hyper-parameters. Additionally, we explore only one additional method of modulation: making some sub-slots partially transparent. It is easy to conceive of other ideas, such as modulating the width of each sub-slot or further increasing the number of intermediate grey steps, all of which serve as significant areas of further research from both modeling and experimental perspectives.

\section*{Data Availability}
The data that support the findings of this study are available from the corresponding author upon reasonable request.

@@

\section*{Funding}
This work was supported by the U.S. National Science Foundation?
